Coherent optical association of atoms into a single molecule

### 2020-11-23 paper.tex
Update on Overleaf.

Here, we demonstrate coherent association of an atom pair to a weakly bound molecule
by two-photon optical Raman transfer via an electronic excited state,
schematically shown in Fig.~\ref{f-theory}a.
The scheme does not rely on a Feshbach resonance,
molecular states bound by a few MHz, or a narrow excited state.
The resulting single molecule is in a well-defined internal quantum state
and predominantly in its motional ground state.
A vibrational state of the electronic excited state $\mathrm{c^3\Sigma^+}(\Omega = 1)$
is used as the intermediate state in the Raman scheme,
and is chosen to minimize photon scattering during Raman Rabi oscillations.
To reduce photon scattering and sensitivity to laser intensity noise further,
we choose the initial and final states to balance the two Rabi frequencies as much as possible.
This system-independent approach creates new molecules atom-by-atom
with full quantum state control.

@@

To find the optimal intermediate state, we perform a calculation of the Raman Rabi frequency $\Omega_R$
and scattering rate $\Gamma_s$ at different detunings from the atomic threshold
taking into account of all states of
the $\mathrm{c^3\Sigma^+}(\Omega = 1)$ excited molecular state potential~\cite{Grochola2011}
and the continuum~\cite{Liu2017}.
This calculation shows that $\Omega_R/\Gamma_s$
can be made larger for more deeply bound states compared to weakly bound states
at a cost of a smaller $\Omega_R$, as shown in Fig.~\ref{f-theory}b;
see Supplementary Material for details.
As a result, we choose the $v'=0$ level of $\mathrm{c^3\Sigma^+}(\Omega = 1)$
as an intermediate state to drive the Raman transition.

@@

To identify a suitable target molecular state, we carry out coupled-channel calculations of the near-threshold bound states, as described in the Supplemental Material.
Choosing a bound state with similar spin character to the atomic state  minimizes the sensitivity of the transition frequency to magnetic field.
A suitable state with this character is predicted about 763 MHz below the $\ket{\uparrow_{\Na} \downarrow_{\Cs}}$ threshold.
The coupled-channel calculations show that this target molecular state has lower overlap with the intermediate state, compared to bound states from other hyperfine combinations.
% For the target molecular state, the spin state is ideally similar to the initial spin state in order to minimize sensitivity to the magnetic field.
% We find a target spin state predominantly in the initial spin state
% that also has the advantage of having a reduced sensitivity
% to laser intensity noise because of a larger %$\Omega_a/\Omega_b$ as compared to other states.
% This reduces the intensity stability requirement to $5~\mathrm{\%}$
% instead of $0.3~\mathrm{\%}$ which is typical for other states.
% In addition to the increased atomic coupling, $ \Omega_a $,
% Coupled-channel calculations show that this target molecular state with similar spin composition also has reduced Rabi frequency, $ \Omega_m $, with the intermediate state when compared to bound states of the other spin compositions.
This further increases the ratio $\Omega_a/\Omega_m$ to about 0.05 when starting from atoms in the $\ket{\uparrow_{\Na} \downarrow_{\Cs}}$ hyperfine combination.
% $\ket{\uparrow_{\Na}\uparrow_{\Cs}}$ and $\ket{\downarrow_{\Na}\downarrow_{\Cs}} $ bound states.
Compared to 0.003
with the other combinations, this relaxes the intensity stability requirement to the few percent level. % Thus, instead of a required intensity stability of $0.3 ~\mathrm{\%} $ for the 4422 or 3311 combination, the 3322 combination only requires the intensity to be stabilized to $ 5~\mathrm{\%} $.
% Thus, we choose the $\ket{\uparrow_{\Na} \downarrow_{\Cs}}$ spin combination as our initial state and drive to the first bound state for the $\ket{\uparrow_{\Na} \downarrow_{\Cs}}$ spin combination.
% \textcolor{blue}{(clean up the paragraph some more).} %(We might want to mention that those ratios are for 80 kHz spherical trap if we want to give more details about the coupled-channel calculation anywhere...)

@@

%% Transfer scheme
% After the atoms are prepared in the $\ket{\uparrow_{\Na}\uparrow_{\Cs}} $ hyperfine combination, we then perform the Raman transfer.
To perform the Raman transfer of an atom pair to the target weakly bound molecular state,
we use the tweezer beam itself as the Raman beams by turning on two frequencies
in the tweezer during the Raman pulse, as shown in Fig.~\ref{f-raman}b inset.
The dual use of the tweezer beam not only eliminates additional scattering sources
or undesired laser frequencies,
but also allows a tight focus to maximize the Raman Rabi frequency
and minimize the transfer time.
Furthermore, we use a Bragg grating with a linewidth (FWHM) of $50~\mathrm{GHz}$
to filter the laser spectrum generated by a fiber amplifier
that is seeded with a $1037~\mathrm{nm}$ external cavity diode laser.
We observe a reduction of the scattering rate by a factor of $2$
due to suppression of the broadband amplified spontaneous emission (ASE) from the laser
that couples to other excited states.
After the total tweezer power is set to the desired value,
we smoothly ramp down the power of one frequency in the tweezer
while simultaneously ramping up the power of the other frequency
so that the total tweezer power remains unchanged.
Both frequencies are kept on for a specified duration before the process is reversed
and the tweezer returns to a single frequency.

@@

We choose the tweezer frequency to be far detuned (by $145 ~\mathrm{GHz}$)
from the $v' = 0$ line. Guided by the coupled-channel calculations,
we locate the Raman resonance for the atoms-to-molecule transition at
$770.57150(9) ~\mathrm{MHz}$ with about $3.75~\mathrm{mW}$ tweezer power,
as shown in Fig.~\ref{f-raman}a.
% (We can maybe add information about the prediction here?)
%% Prediction
% This excited state used in the Raman transition was measured in our previous experiment using photoassociation to be at $288560 GHz$ from our atomic state. The ground molecular state has not been observed previously in experimentally. Based on our measurement of FB resonance, interaction shift and the binding energy of the 4422 bound state. Theory prediction was at $770.1 MHz$.
% The background level of $31~\mathrm{\%}$ corresponds to the probability of preparing the two atoms in the relative motional ground state.
% When the atoms are transferred into the molecule state by the Raman transition, there is a decrease in the two body survival since the resulting molecule is dark to our imaging sequence. % directly detected by our imaging step.
The molecular state is dark to the imaging step,
so successful transfer of the atoms to the molecular state is detected as loss.
We observe a Fourier-limited linewidth, which is evidence of a coherent transfer.
In order to verify the coherence of the transfer directly,
we fix the two-photon detuning on resonance and scan the pulse time.
Fig.~\ref{f-raman}b shows the observed coherent Rabi oscillation between the atomic and molecular states.
Fitting the data with a decaying Rabi oscillation suggests that
$69~\mathrm{\%}$ of atoms initially in the motional ground state are transferred into the molecular state after a $\pi$ pulse.
This transfer efficiency is limited mainly by the molecular lifetime,
which can be measured directly by preparing the molecule with a $\pi $ pulse
and then using a second $\pi$ pulse to dissociate the molecule back to atoms
after a variable wait time.
The result in Fig.~\ref{f-lifetime}a shows a molecular lifetime of $0.199(9)~\mathrm{ms}$
consistent with the decay of the Rabi oscillation.
We obtain the Raman Rabi frequency by fitting our measurements to a model
that includes a Raman Rabi frequency and
a finite lifetime for the molecular state, as shown in Fig.~\ref{f-raman}a and b.
We account for the effect of atomic state loss by measuring the one-body and
two-body lifetime of the atoms directly without turning on the second frequency,
as shown in Fig.~\ref{f-lifetime}b.
The fit gives a Raman Rabi frequency of $2\pi\times3.28(4)~\mathrm{kHz}$.

The efficiency of the transfer is lower than expected
because the ratio of the molecular scattering rate to the Rabi frequency
is 10 times larger than predicted.
Based on the discussion above, if this discrepancy arises from the $v'=0$ excited state,
it can be due either to a high ratio $\Omega_m / \Omega_a$ or to a large $\Gamma_e$.
Additionally, coupling to other excited states can add an offset to
both the Raman Rabi frequency and the scattering rate and thus affect their ratio.

@@

In order to verify whether any one of these known sources are the origin of the reduced transfer efficiency,
we measured the properties of the Raman resonance as a function of the tweezer power and single-photon detuning.
These dependencies allow us to experimentally determine the Rabi frequencies,
$ \Omega_a $, $\Omega_m $ and how much of the scattering, Stark shift,
or Raman Rabi frequency comes from the $ v' = 0$ intermediate state.

First we look at the change in resonance frequency to determine $\Omega_m$.
We observe that the resonance frequency depends linearly on the tweezer power due to the differential light shift between the atomic and molecular state.
When we vary the tweezer frequency around the $v'=0$ intermediate state,
we can further observe a $1/\Delta$ component
and a constant background in the experimentally explored region, as shown in Fig.~\ref{f-det}a.
The background is caused by coupling to other excited states that are further away in energy.
The $1/\Delta$ component, however, is due to the coupling between the molecular state
and the $v'=0$ intermediate state.
From this measurement, we can extract a $\Omega_m$ of
$2\pi\times72.32(4) ~\mathrm{MHz}/\sqrt{\mathrm{mW}}$.
% or
% $2\pi\times140.06(8) ~\mathrm{MHz}$ for the $3.75~\mathrm{mW}$ tweezer power used above.
This number is close to the value of
$2\pi\times40.7 ~\mathrm{MHz}/\sqrt{\mathrm{mW}}$ calculated from theory. \todo{ref/sm theory}

@@

In order to calculate the ratio $\Omega_m/\Omega_a$,
we now need to extract $ \Omega_a $.
We do this by measuring the dependence of the Raman Rabi frequency on power and detuning.
% which depends on both $\Omega_m$ and $\Omega_a$.
The Raman Rabi frequency shows a non-linear dependency on the tweezer power
due to the change in the atomic wavefunction caused by
tighter confinement at higher power, as shown in Fig.~\ref{f-det}b.
As discussed before, for weakly interacting particles,
$\Omega_a$ scales as $P^{3/8}$.
However, due to the strong interaction between the two atoms in the $\ket{\uparrow_{\text{Na}}\downarrow_{\text{Cs}}}$ state, this approximation breaks down.
Instead, coupled-channel calculations show that the scaling
is very well approximated by $P^{0.29}$ within the range of confinement in our experiment.
Combined with the standard intensity factor, the Raman Rabi frequency should scale as $P^{1.29}$,
which fits well to our experimental result, as shown in Fig.~\ref{f-det}c.
Similar to the light shift, the detuning dependency of the Raman Rabi frequency
is determined by a constant background component and
a $v'=0$ component that scales as $1/\Delta$.
The $v'=0$ component of the Raman Rabi frequency at our detuning is
$2\pi\times1.02(2)~\mathrm{kHz\cdot mW^{-1.29}}$,
or $2\pi \times 5.6(1)~\mathrm{kHz}$ at $3.75~\mathrm{mW}$ tweezer power.
Together with the $\Omega_m$ measured above, the Rabi frequency, $ \Omega_a $, is
$2\pi \times 12.1(3)~\mathrm{MHz}$.
This gives a matrix-element ratio of $11.6(3)$,
which is in fact better than the theory prediction of $23.8$ (Table \ref{tab:rabi_freqs}).
Therefore, this should not cause the ratio of the Raman Rabi frequency to scattering rate
from the $v'=0$ state to be higher than expected.
Furthermore, we independently measure the natural linewidth of the $v'=0$ excited state to be no larger than $20~\mathrm{MHz}$ using photoassociation (PA) spectroscopy.
This suggests that the excited-state linewidth should not cause
a stronger than expected scattering from $v'=0$ state either.

\begin{table}[ht]
  \centering
  \begin{tabular}{c|c|c}
    & Experiment & Theory \\ \hline
    $ \Omega_m $ & $2\pi \times 140.06(8) ~\mathrm{MHz} $ & $2\pi \times 78.9 ~\mathrm{MHz}$ \\
    $\Omega_a$ & $2\pi \times 12.1(3) ~\mathrm{MHz}$ & $2\pi \times 3.32 ~\mathrm{MHz}$ \\
    $\Omega_m/\Omega_a$ & $11.6(3)$ & $ 23.8$
  \end{tabular}
  \caption{Comparison between theory and experiment of the Rabi frequencies $\Omega_m$ and $\Omega_a$ at $3.75$ mW tweezer power. The experimentally measured ratio $\Omega_m/\Omega_a$ is smaller than the theory prediction.}
  \label{tab:rabi_freqs}
\end{table}

With the $ v' = 0 $ state ruled out as the source of discrepancy between experiment and theory,
we now consider the background effects from other states with larger single-photon detuning.
In the Raman Rabi frequency fit,
the fitted background is of opposite sign from the Raman Rabi frequency
for single-photon detunings red of the $v' = 0 $ transition.
Thus, this background reduces the Raman Rabi frequency by about $30~\mathrm{\%}$
at the current detuning.
However, this difference is not enough to explain the discrapancy of more than a factor of $10$
present in the experiment.
Due to the change in sign of the Raman Rabi frequency as a function of detuning
when crossing a resonance, the same background will increase the Raman Rabi frequency
for positive detunings from the $v' = 0$ transition.
Unfortunately, we observe additional nearby excited states
belonging to a different electronically excited state at higher frequencies
which prevent the blue side of the transition from being be usable for the Raman transition.

\todo{change scattering to decoherence? since the fluctuation of light shift
  does not lead to scattering but only decherence.}
These results suggest that the decoherence or loss we observe during the Raman transition
comes from either a higher than expected background scattering rate
or a different intrinsic or technical source for which we have not accounted for.
We observe a decrease in the coherence time by a factor of 2 without the ASE filter,
suggesting the spectral purity of the laser is a significant source of scattering.
Other sources that can contribute to the decoherence include
the stability of the tweezer power and the magnetic field.
Based on the ratio of the Raman Rabi frequency to light shift, shown in Fig.~\ref{f-det}c,
the requirement on the tweezer power stability is $0.8\mathrm{\%}$ at $3.75~\mathrm{mW}$. We stabilize the power to $0.1\mathrm{\%}$, so this should not be a major source of decoherence.
Similarly, we measured a Zeeman shift of $42.2(2)~\mathrm{kHz/G}$
which does not cause significant decoherence from the measured magnetic field
fluctuation of $\sim1.5~\mathrm{mG}$.

@@

In conclusion, we have formed a weakly bound NaCs molecule in an optical tweezer
by optical Raman transfer.
A theoretical investigation including all excited states of $\mathrm{c^3\Sigma^+}(\Omega = 1)$,
the excited atomic continuum, and coupled-channel ground state wavefunctions indicated
better transfer efficiency using a deeply bound intermediate state
and the $\ket{\uparrow_{\Na} \downarrow_{\Cs} }$ spin state as the initial and final states.
Using these theoretical insights, we located the weakly bound state
and coherently associated the atoms into a weakly bound molecule.
Our transfer efficiency is limited by an unknown scattering source
resulting in measured scattering rates over $10$ times larger than theoretical predictions.
Despite this limitation, the transfer efficiency may be further improved
by increasing the ratio of the up-leg to down-leg Rabi frequency
$\Omega_a/\Omega_m$, for example by driving to more deeply bound states.
There may also be a better choice of single-photon detuning to increase the Raman Rabi frequency,
since our location results in about $30~\mathrm{\%}$ cancellation of the Raman Rabi frequency
due to an offset of unknown origin.

Our technique can be applied to form a more diverse set of molecular species,
since it does not rely on a magnetic Feshbach resonance, states bound by a few MHz,
or a narrow excited state. The formation of a weakly bound molecule is a key step
in forming rovibrational ground state molecules.
Combined with real-time rearrangement~\cite{Barredo2016, Endres2016},
defect-free arrays of highly controlled molecules comprise a promising
and flexible platform for quantum simulation and quantum computing applications.

@@

\begin{acknowledgments}
  We would like to thank Bo Gao,  Paul Julienne, and Rosario Gonzalez-Ferez for discussion. This work is supported by the NSF~(PHY-1806595), the AFOSR~(FA9550-19-1-0089), ARO DURIP (W911NF1810194) and the Arnold and Mabel Beckman foundation. J.~T.~Z. is supported by a National Defense Science and Engineering Graduate Fellowship. W.~C. is supported by a Max Planck-Harvard Research Center for Quantum Optics fellowship. K.~W. is supported by an NSF GRFP fellowship. J.~M.~H. is supported by the U.K. Engineering and Physical Sciences Research Council (EPSRC) Grants No.\ EP/N007085/1, EP/P008275/1 and EP/P01058X/1.
\end{acknowledgments}

>>>>

Here, we demonstrate coherent association of an atom pair to a weakly bound molecule
by two-photon optical Raman transfer via an electronic excited state,
schematically shown in Fig.~\ref{f-theory}a.
The scheme does not rely on a Feshbach resonance,
molecular states bound by a few MHz, or a narrow excited state.
The resulting single molecule is in a well-defined internal quantum state
and predominantly in its motional ground state.
A vibrational state of the electronic excited state $\mathrm{c^3\Sigma^+}(\Omega = 1)$
is used as the intermediate state in the Raman scheme,
and is chosen to minimize photon scattering during Raman Rabi oscillations.
To reduce photon scattering and sensitivity to laser intensity noise further,
we choose the initial and final states to balance the two Rabi frequencies as much as possible.
This system-independent approach creates molecules atom-by-atom
with full quantum state control.

@@

To find the optimal intermediate state, we perform a calculation of the Raman Rabi frequency $\Omega_R$
and scattering rate $\Gamma_s$ at different detunings from the atomic threshold
taking into account of all states of
8 excited molecular state potentials~\cite{Korek2007, Grochola2011, Zaharova2009, Grochola2010, Zabawa2012}
and the continuum~\cite{Liu2017}.
This calculation shows that $\Omega_R/\Gamma_s$
can be made larger for more deeply bound states compared to weakly bound states
at a cost of a smaller $\Omega_R$, as shown in Fig.~\ref{f-theory}b;
see Supplementary Material for details.
As a result, we choose the $v'=0$ level of $\mathrm{c^3\Sigma^+}(\Omega = 1)$
as the closest intermediate state to drive the Raman transition.

@@

To identify a suitable target molecular state, we carry out coupled-channel calculations of the near-threshold bound states, as described in the Supplemental Material.
Choosing a bound state with similar spin character to the atomic state  minimizes the sensitivity of the transition frequency to magnetic field.
A suitable state with this character is predicted about 763 MHz below the $\ket{\uparrow_{\Na} \downarrow_{\Cs}}$ threshold.
%The coupled-channel calculations show that this target molecular state has lower overlap with the intermediate state, compared to bound states from other hyperfine combinations.
% For the target molecular state, the spin state is ideally similar to the initial spin state in order to minimize sensitivity to the magnetic field.
% We find a target spin state predominantly in the initial spin state
% that also has the advantage of having a reduced sensitivity
% to laser intensity noise because of a larger %$\Omega_a/\Omega_b$ as compared to other states.
% This reduces the intensity stability requirement to $5~\mathrm{\%}$
% instead of $0.3~\mathrm{\%}$ which is typical for other states.
% In addition to the increased atomic coupling, $ \Omega_a $,
% Coupled-channel calculations show that this target molecular state with similar spin composition also has reduced Rabi frequency, $ \Omega_m $, with the intermediate state when compared to bound states of the other spin compositions.
The ratio $\Omega_a/\Omega_m$ increases to about 0.013 when starting from atoms in the $\ket{\uparrow_{\Na} \downarrow_{\Cs}}$ hyperfine combination.
% $\ket{\uparrow_{\Na}\uparrow_{\Cs}}$ and $\ket{\downarrow_{\Na}\downarrow_{\Cs}} $ bound states.
Compared to 0.003
with the other combinations, this relaxes the intensity stability requirement to the percent level. % Thus, instead of a required intensity stability of $0.3 ~\mathrm{\%} $ for the 4422 or 3311 combination, the 3322 combination only requires the intensity to be stabilized to $ 5~\mathrm{\%} $.
% Thus, we choose the $\ket{\uparrow_{\Na} \downarrow_{\Cs}}$ spin combination as our initial state and drive to the first bound state for the $\ket{\uparrow_{\Na} \downarrow_{\Cs}}$ spin combination.
% \textcolor{blue}{(clean up the paragraph some more).} %(We might want to mention that those ratios are for 80 kHz spherical trap if we want to give more details about the coupled-channel calculation anywhere...)

@@

%% Transfer scheme
% After the atoms are prepared in the $\ket{\uparrow_{\Na}\uparrow_{\Cs}} $ hyperfine combination, we then perform the Raman transfer.
To perform the Raman transfer of an atom pair to the target weakly bound molecular state,
we use the tweezer beam itself as the Raman beams by turning on two frequencies
in the tweezer during the Raman pulse, as shown in Fig.~\ref{f-raman}b inset.
The dual use of the tweezer beam not only eliminates additional scattering sources
or undesired laser frequencies,
but also allows a tight focus to maximize the Raman Rabi frequency
and minimize the transfer time.
Furthermore, we use two Bragg gratings, each with a linewidth (FWHM) of $50~\mathrm{GHz}$,
to filter the laser spectrum generated by a fiber amplifier
that is seeded with a $1037~\mathrm{nm}$ external cavity diode laser.
We observe a reduction of the scattering rate by a factor of $2$
due to suppression of the broadband amplified spontaneous emission (ASE) from the laser
that couples to other excited states.
After the total tweezer power is set to the desired value,
we smoothly ramp down the power of one frequency in the tweezer
while simultaneously ramping up the power of the other frequency
so that the total tweezer power remains unchanged.
Both frequencies are kept on for a specified duration before the process is reversed
and the tweezer returns to a single frequency.

@@

We choose the tweezer frequency to be far detuned (by $145 ~\mathrm{GHz}$)
from the $v' = 0$ line. Guided by the coupled-channel calculations,
we locate the Raman resonance for the atoms-to-molecule transition at
$770.57150(9) ~\mathrm{MHz}$ with about $3.75~\mathrm{mW}$ tweezer power focused down to a waist of $ 0.9~\mathrm{\mu m}$,
as shown in Fig.~\ref{f-raman}a.
% (We can maybe add information about the prediction here?)
%% Prediction
% This excited state used in the Raman transition was measured in our previous experiment using photoassociation to be at $288560 GHz$ from our atomic state. The ground molecular state has not been observed previously in experimentally. Based on our measurement of FB resonance, interaction shift and the binding energy of the 4422 bound state. Theory prediction was at $770.1 MHz$.
% The background level of $31~\mathrm{\%}$ corresponds to the probability of preparing the two atoms in the relative motional ground state.
% When the atoms are transferred into the molecule state by the Raman transition, there is a decrease in the two body survival since the resulting molecule is dark to our imaging sequence. % directly detected by our imaging step.
The molecular state is dark to the imaging step,
so successful transfer of the atoms to the molecular state is detected as loss of atoms.
We observe a Fourier-limited linewidth, which is evidence of a coherent transfer.
In order to verify the coherence of the transfer directly,
we fix the two-photon detuning on resonance and scan the pulse time.
Fig.~\ref{f-raman}b shows the observed coherent Rabi oscillation between the atomic and molecular states.
Fitting the data with a decaying Rabi oscillation suggests that
$69~\mathrm{\%}$ of atoms initially in the motional ground state are transferred into the molecular state after a $\pi$ pulse.
This transfer efficiency is limited mainly by the molecular lifetime,
which can be measured directly by preparing the molecule with a $\pi $ pulse
and then using a second $\pi$ pulse to dissociate the molecule back to atoms
after a variable wait time.
The result in Fig.~\ref{f-lifetime}a shows a molecular lifetime of $0.199(9)~\mathrm{ms}$
consistent with the decay of the Rabi oscillation.
We obtain the Raman Rabi frequency by fitting our measurements to a model
that includes a Raman Rabi frequency and
a finite lifetime for the molecular state, as shown in Fig.~\ref{f-raman}a and b.
We account for the small effect of atomic state loss by measuring the one-body and
two-body lifetime of the atoms directly without turning on the second frequency,
as shown in Fig.~\ref{f-lifetime}b.
The fit including all these effects gives a Raman Rabi frequency of $2\pi\times3.28(4)~\mathrm{kHz}$.

The efficiency of the transfer is lower than expected
because the ratio of the molecular scattering rate to the Rabi frequency
is 10 times larger than predicted. If this discrepancy arises from the $v'=0$ excited state,
it can be due either to a high ratio $\Omega_m / \Omega_a$ or to a large $\Gamma_e$.
Additionally, coupling to other excited states can add an offset to
both the Raman Rabi frequency and the scattering rate and thus affect their ratio.

@@

In order to verify whether any one of these sources are the origin of the reduced transfer efficiency,
we measured the properties of the Raman resonance as a function of the tweezer power and single-photon detuning.
These dependencies allow us to experimentally determine the Rabi frequencies,
$ \Omega_a $, $\Omega_m $ and how much of the scattering, Stark shift,
or Raman Rabi frequency comes from the $ v' = 0$ intermediate state.

First we look at the change in resonance frequency to determine $\Omega_m$.
We observe that the resonance frequency depends linearly on the tweezer power due to the differential light shift between the atomic and molecular state.
When we vary the tweezer frequency around the $v'=0$ intermediate state,
we can further observe a $1/\Delta$ component
and a constant background in the experimentally explored region, as shown in Fig.~\ref{f-det}a.
The background is caused by coupling to other excited states that are further away in energy.
The $1/\Delta$ component, however, is due to the coupling between the molecular state
and the $v'=0$ intermediate state.
From this measurement, we can extract a $\Omega_m$ of
$2\pi\times72.32(4) ~\mathrm{MHz}/\sqrt{\mathrm{mW}}$.
% or
% $2\pi\times140.06(8) ~\mathrm{MHz}$ for the $3.75~\mathrm{mW}$ tweezer power used above.
This number is close to the value of
$2\pi\times296 ~\mathrm{MHz}/\sqrt{\mathrm{mW}}$ calculated from theory. \todo{ref/sm theory}

@@

In order to calculate the ratio $\Omega_m/\Omega_a$,
we now need to extract $ \Omega_a $.
We do this by measuring the dependence of the Raman Rabi frequency on power and detuning.
% which depends on both $\Omega_m$ and $\Omega_a$.
The Raman Rabi frequency shows a non-linear dependency on the tweezer power
due to the change in the atomic wavefunction caused by
tighter confinement at higher power, as shown in Fig.~\ref{f-det}b.
As discussed before, for weakly interacting particles,
$\Omega_a$ scales as $P^{3/8}$.
However, due to the strong interaction between the two atoms in the $\ket{\uparrow_{\text{Na}}\downarrow_{\text{Cs}}}$ state, this approximation breaks down.
Instead, coupled-channel calculations show that the scaling
is very well approximated by $P^{0.29}$ within the range of confinement in our experiment.
Combined with the standard intensity factor, the Raman Rabi frequency should scale as $P^{1.29}$,
which fits well to our experimental result, as shown in Fig.~\ref{f-det}c.
Similar to the light shift, the detuning dependency of the Raman Rabi frequency
is determined by a constant background component and
a $v'=0$ component that scales as $1/\Delta$.
The $v'=0$ component of the Raman Rabi frequency at our detuning is
$2\pi\times1.02(2)~\mathrm{kHz\cdot mW^{-1.29}}$,
or $2\pi \times 5.6(1)~\mathrm{kHz}$ at $3.75~\mathrm{mW}$ tweezer power.
Together with the $\Omega_m$ measured above, the Rabi frequency, $ \Omega_a $, is
$2\pi \times 12.1(3)~\mathrm{MHz}$.
This gives a matrix-element ratio of $11.6(3)$,
which is in fact better than the theory prediction of $23.8$ (Table \ref{tab:rabi_freqs}).
Therefore, this should not cause the ratio of the Raman Rabi frequency to scattering rate
from the $v'=0$ state to be higher than expected.
Furthermore, we independently measure the natural linewidth of the $v'=0$ excited state to be no larger than $20~\mathrm{MHz}$ using photoassociation (PA) spectroscopy, which cannot explain the excess scattering either.

\begin{table}[ht]
  \centering
  \begin{tabular}{c|c|c}
    & Experiment & Theory \\ \hline
    $ \Omega_m $ & $2\pi \times 140.06(8) ~\mathrm{MHz} $ & $2\pi \times 573 ~\mathrm{MHz}$ \\
    $\Omega_a$ & $2\pi \times 12.1(3) ~\mathrm{MHz}$ & $2\pi \times 7.37 ~\mathrm{MHz}$ \\
    $\Omega_m/\Omega_a$ & $11.6(3)$ & $ 77.7$
  \end{tabular}
  \caption{Comparison between theory and experiment of the Rabi frequencies $\Omega_m$ and $\Omega_a$ at $3.75$ mW tweezer power. The experimentally measured ratio $\Omega_m/\Omega_a$ is smaller than the theory prediction.}
  \label{tab:rabi_freqs}
\end{table}

With the contribution of the $ v' = 0 $ state to the Raman Rabi frequency and scattering investigated,
we now consider the background effects from other states with larger single-photon detuning.
In the Raman Rabi frequency fit,
the fitted background is of opposite sign from the Raman Rabi frequency
for single-photon detunings red of the $v' = 0 $ transition.
Thus, this background reduces the Raman Rabi frequency by about $30~\mathrm{\%}$
at the current detuning.
However, this difference is not enough to explain the discrapancy of more than a factor of $10$
present in the experiment.
Due to the change in sign of the Raman Rabi frequency as a function of detuning
when crossing a resonance, the same background will increase the Raman Rabi frequency
for positive detunings from the $v' = 0$ transition.
Unfortunately, we observe additional nearby excited states
belonging to a different electronically excited state at higher frequencies
which prevent the blue side of the transition from being be usable for the Raman transition.

\todo{change scattering to decoherence? since the fluctuation of light shift
  does not lead to scattering but only decherence.}
These results suggest that the decoherence or loss we observe during the Raman transition
comes from either a higher background scattering rate of an unknown source
or a different intrinsic or technical source for which we have not accounted for.
We observe a decrease in the coherence time by a factor of 2 without the ASE filters. This
suggests the spectral purity of the laser is a significant source of scattering, but does not explain the full amount. 
Other sources that can contribute to the decoherence include
the stability of the tweezer power and the magnetic field.
Based on the ratio of the Raman Rabi frequency to light shift, shown in Fig.~\ref{f-det}c,
the requirement on the tweezer power stability is $0.8\mathrm{\%}$ at $3.75~\mathrm{mW}$. We stabilize the power to $0.1\mathrm{\%}$, so this should not be a major source of decoherence.
Similarly, we measured a Zeeman shift of $42.2(2)~\mathrm{kHz/G}$
which does not cause significant decoherence from the measured magnetic field
fluctuation of $\sim1.5~\mathrm{mG}$.

@@

In conclusion, we have formed a weakly bound NaCs molecule in an optical tweezer
by optical Raman transfer.
A theoretical investigation including 8 excited state potentials,
the excited atomic continuum, and coupled-channel ground state wavefunctions indicated
better transfer efficiency using a deeply bound intermediate state
and the $\ket{\uparrow_{\Na} \downarrow_{\Cs} }$ spin state as the initial and final states.
Using these theoretical insights, we located the weakly bound state
and coherently associated the atoms into a weakly bound molecule. Currently, 
Our transfer efficiency is limited by an unknown scattering source
resulting in measured scattering rates over $10$ times larger than theoretical predictions.
Despite this limitation, the transfer efficiency may be further improved
by increasing the ratio of the up-leg to down-leg Rabi frequency
$\Omega_a/\Omega_m$, for example by driving to more deeply bound states.

Our technique can be applied to form a more diverse set of molecular species,
since it does not rely on a magnetic Feshbach resonance, states bound by a few MHz,
or a narrow excited state. The formation of a weakly bound molecule is a key step
in forming rovibrational ground state molecules. By scaling up to many optical tweezers, large arrays with arbitrary geometry of highly controlled molecules can be achieved.
%Combined with real-time rearrangement~\cite{Barredo2016, Endres2016},
%defect-free arrays of highly controlled molecules comprise a promising
%and flexible platform for quantum simulation and quantum computing applications.

@@

\begin{acknowledgments}
  We would like to thank Rosario Gonzalez-Ferez, Bo Gao, and Paul Julienne \textcolor{red}{acknowledge getting TDM} for discussion. This work is supported by the NSF~(PHY-1806595), the AFOSR~(FA9550-19-1-0089), ARO DURIP (W911NF1810194) and the Arnold and Mabel Beckman foundation. J.~T.~Z. is supported by a National Defense Science and Engineering Graduate Fellowship. W.~C. is supported by a Max Planck-Harvard Research Center for Quantum Optics fellowship. K.~W. is supported by an NSF GRFP fellowship. J.~M.~H. is supported by the U.K. Engineering and Physical Sciences Research Council (EPSRC) Grants No.\ EP/N007085/1, EP/P008275/1 and EP/P01058X/1.
\end{acknowledgments}
